\subsection{NAME\label{NAME}\index{NAME}}


TRepid

\subsection{DESCRIPTION\label{DESCRIPTION}\index{DESCRIPTION}}


Main class for simulation of Transposon evolution

\subsubsection*{Primary functions\label{Primary_functions}\index{Primary functions}}
\paragraph*{prepare()\label{prepare_}\index{prepare()}}


This function will load a previously existing population from disk, if
one exists, or initialize a new population of otherwise. It will also
make sure all required options are collected from trepid.conf, or that
defaults are in usad.

\paragraph*{simulate()\label{simulate_}\index{simulate()}}


This function runs a simulation, consisting of several generations of
the Host population, cf. defined in trepid.conf

\paragraph*{save()\label{save_}\index{save()}}


This function saves the population from memory to disk.

\paragraph*{clean()\label{clean_}\index{clean()}}


This function erases the population from memory.

\paragraph*{run()\label{run_}\index{run()}}


This is just a quick way to run automatically. It calls prepare(), then
simulate().

\subsubsection*{Secondary functions\label{Secondary_functions}\index{Secondary functions}}
\paragraph*{non\_interactive\_preload()\label{non_interactive_preload_}\index{non\ interactive\ preload()}}


This function does the initial configuring before saving options are
parsed. This includes printing a header for the simulation and making
sure the data directories are present and accessible.

\paragraph*{interactive\_preload()\label{interactive_preload_}\index{interactive\ preload()}}


This function asks questions on what to save after the simulation, if
interactiveness is permitted. A non-interactive simulation will occur
if any of the following occur:



- all options are explicitly specified in trepid.conf
- the "interactive" option is set to 0 in trepid.conf

\paragraph*{save\_check()\label{save_check_}\index{save\ check()}}


This function parses variables that are collected either from
interactive\_preload or trepid.conf, and make sure they're usable.

